Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2013-01-22 ASA2013/asa2013.tex
la2pdf commit - 2013:01:22	14:40:42	(Tue22.Jan)
la2pdf commit - 2013:01:22	15:37:25	(Tue22.Jan)

\newcommand*\A{\mat A}
\newcommand*\B{\mat B}
\newcommand*\C{\mat C}
\newcommand*\E{\mat E}
% \renewcommand*\H{\mat H}
\renewcommand*\P{\mat P}
\newcommand*\eP{\mat{\hat P}}
\newcommand*\R{\mat R}
\newcommand*\Ri{\R^{-1}}
\newcommand*\eR{\mat{\hat R}}
\newcommand*\eRi{\hat{\mat R}\,\!^{-1}}
\newcommand*\Navg{N_\text{avg}}
\newcommand*\W{\mat W}
\newcommand*\X{\mat X}
\newcommand*\Xd{\X_{\!\Delta}}
\newcommand*\Y{\mat Y}

@@

O($N_K N_L L^2$) and the inversion of O($L^3$)

@@

The Low Complexity Adaptive (LCA) beamformer is another take on the optimization problem in (\ref{mvdr_def}). Instead of calculating the weights like in (\ref{weights}), it simply computes the beamformer output for each window in a collection of such, and finally applies the one that best fulfils the given optimization criterion. If we let $\w_p$ be the $p$'th of a total of $P$ windows, then this can be formulated as:
\begin{gather}
\argmin{p}\ E\Big\{\big|\w_p\H\x[n]\big|^2\Big\} \qquad\text{subject to}\qquad \w_p\H\1 = 1\label{lca_def}. 
% \vec w[n] = \frac{\Ri[n]\1}{\1\T\Ri[n]\1},\label{weights}
\end{gather}
Note that (\ref{mvdr_ref}) and (\ref{lca_ref}) is essentially the same criterion.

<< AVERAGING >>

@@

<< AVERAGING >>

@@

\begin{figure}[h]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/plot_holmengraa_L16_Navg1.pdf}%
\caption{Holmengraa.}\label{mvdr_implementation}
\end{figure}

>>>>

\newcommand*\A{\mat A}
\newcommand*\B{\mat B}
\newcommand*\C{\mat C}
\newcommand*\E{\mat E}
% \renewcommand*\H{\mat H}
\renewcommand*\P{\mat P}
\newcommand*\eP{\mat{\hat P}}
\newcommand*\R{\mat R}
\newcommand*\Ri{\R^{-1}}
\newcommand*\eR{\mat{\hat R}}
\newcommand*\eRi{\hat{\mat R}\,\!^{-1}}
\newcommand*\Navg{N_\text{avg}}
\newcommand*\W{\mat W}
\newcommand*\X{\mat X}
\newcommand*\Xd{\X_{\!\Delta}}
\newcommand*\Y{\mat Y}
\renewcommand*\B{\mat B}

@@

Complexity: O($N_K N_L L^2$) and the inversion of O($L^3$)

@@

For larger systems the inversion step will completely dominate the computation time. Although the dimensionality of the coveriance matrix was reduced to $L$ due to subarray averaging, we can reduce it further by moving to the frequency domain. If the data is narrowband enough there is a very close relation between the frequency conent and angles of arrival in the spatial domain; the zero-frequency component will correspond to broadside, and    component corresponding to broadside and increasing frequencies  This is usually handled by reducing the dimensionality of the covariance matrix to

\begin{gather}
\x_\text{BS}[n] = \B\x[n], \qquad \B\in \mathbb{C}^{N,M}, \qquad \text{where} \qquad [\B]_{p,q} = \frac{1}{\sqrt{M}} e^{-j2\pi\,p\,q/M}.\label{beamspace}
\end{gather}

Complexity: To frequency domain: O($N_b\,L$). Build $R_\text{BS}$, O($N_b^2\,N_L\,N_K$). Inversion: O($N_b^3$).

@@

@@

\begin{figure}[!h]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/plot_holmengraa_L16_Navg1.pdf}%
\caption{Holmengraa.}\label{mvdr_implementation}
\end{figure}
